---
title: "training_data_sentiment_analysis"
output: html_document
date: "2023-06-16"
---

# Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(syuzhet) # allows use of sentiment analysis functions
library(ggplot2) # allows use of ggplot functions
library(jsonlite) # allows us to read json files
library(dplyr) # allows use of pipe operator
library(tidyverse) # allows us to do lots of fundamental data science tasks (ex. read_csv)
library(tidytext) # fixes loading nrc chunk 
library(here) # allows us to cut out long file paths (ex. "users/connor/dowloads/etc")
```

# Import "training.csv" file
```{r}
training_data <- read_csv(here("data/training.csv"))
head(training_data)
```

# Create vector from text column
```{r}
training_vector <- as.character(training_data$text)
head(training_vector)
```
# Run NRC sentiment analysis function on training data
```{r}
training_sentiment <- get_nrc_sentiment(training_vector)
head(training_sentiment)
```

# Sum sentiment analysis scores
```{r}
training_sentiment_score <- data.frame(colSums(training_sentiment[,]))
head(training_sentiment_score)
```

# Fix rows and columns for barplot
```{r}
# Viz Prep 1
names(training_sentiment_score) <- 'score'
names(training_sentiment_score)

# Viz Prep 2
training_sentiment_score <- cbind("sentiment"=rownames(training_sentiment_score), training_sentiment_score)
names(training_sentiment_score)

# Viz Prep 3
rownames(training_sentiment_score) <- NULL

training_sentiment_score
```

# Create first visual
```{r}
ggplot(data=training_sentiment_score, aes(x=sentiment, y=score)) +
  geom_bar(aes(fill=sentiment), stat="identity") +
  theme(legend.position="none") +
  xlab("Sentiments") +
  ylab("Scores") +
  ggtitle("Sentiment Analysis on Training Data")
```

# Remove positive and negative sentiment from x axis
```{r}
training_sentiment_score_edited <- training_sentiment_score[1:8,]
training_sentiment_score_edited
```

# Rerun Visualization Code
```{r}

ggplot(data=training_sentiment_score_edited, aes(x=sentiment, y=score))+
  geom_bar(aes(fill=sentiment), stat="identity") +
  theme(legend.position="none")+
  xlab("Sentiments")+
  ylab("Scores")+
  ggtitle("Sentiment Analysis on Training Data")
```

# JUMP: Break up vector into sentences vector
```{r}
training_sentences <- get_sentences(training_vector)
head(training_sentences)
```

# Run sentiment analysis function
```{r}
training_sentences_sentiment <- get_sentiment(training_sentences)
head(training_sentences_sentiment)
```

# Stats on sentiment
```{r}
print("Overall emotional valence in text, positive number indicates positive text")
sum(training_sentences_sentiment)
print("Mean above zero indicates average positive emotional valence")
mean(training_sentences_sentiment)
print("Summary stats of emotional valence")
summary(training_sentences_sentiment)
```

# Plot emotional valence over narrative time, not useful over long texts
```{r}
plot(
  training_sentences_sentiment, 
  type="h", 
  main="Example Plot Trajectory", 
  xlab = "Narrative Time", 
  ylab= "Emotional Valence"
  )
```

# Remove noise from plot using get_percentage_values function
```{r}
percent_vals <- get_percentage_values(training_sentences_sentiment, bins = 10)
plot(
  percent_vals, 
  type="l", 
  main="Training Data Using Percentage-Based Means", 
  xlab = "Narrative Time", 
  ylab= "Emotional Valence", 
  col="red"
  )
```

# Changing the "bins" argument, you can control how many bins the sentences are divided into.
```{r}
percent_vals_20 <- get_percentage_values(training_sentences_sentiment, bins = 20)
plot(
  percent_vals_20, 
  type="l", 
  main="Training Data Using Percentage-Based Means", 
  xlab = "Narrative Time", 
  ylab= "Emotional Valence", 
  col="red"
  )
```

# Get transformed values using get_dct_transform function
```{r}
dct_values <- get_dct_transform(
      training_sentences_sentiment, 
      low_pass_size = 5, 
      x_reverse_len = 100,
      scale_vals = F,
      scale_range = T
      )
```

```{r}

```

